Intercoder ICBEdataset_figure_semantic_embeddings

### 2022-02-03 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
embed

```{r, messages=F, results='hide'}
library(reticulate)
py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
use_python("/home/tlscherer/anaconda3/bin/python")

@@

@@

#devtools::install_github("ropenscilabs/umapr")
library(umapr)
embedding <- umap(sentences_embedding)

@@

library(RColorBrewer)
brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange()
brewer_list <- list() 
for(i in c(11, 1:nrow(brewer_pal_info_df))){
  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
}
posible_colors <- unlist(brewer_list) %>% unique(brewer_list) #%>% sample()

value_normalized=codings_long_agreed_embeded_subset$value_normalized %>% unique() %>% as.factor()
value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
names(value_normalized_colors) = levels(value_normalized)

@@

        facet_wrap( ~ variable_normalized) + 
        theme_bw() +
        theme(legend.position = "none") + 
        geom_label(data=value_means,
                   aes(x=UMAP1,y=UMAP2, fill = value_normalized, label=value_normalized, size=50),inherit.aes=F, # #variable_normalized_count
                   colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")) + 
        labs(
            title = "Variation in Tags by Semantic Embeddings of Source Sentences",
            subtitle = "Sentences Embedding Sentence-BERT, UMAP Projection ",
            caption = ""
        ) +
       scale_color_manual(values = value_normalized_colors) +
       scale_fill_manual(values = value_normalized_colors)

>>>>

To set python, set it in ~/.Renviron. `use_python()` doesn't seem to work as desired. See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).

```{r, messages=F, results='hide'}
library(reticulate)
reticulate::py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

@@

```
The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.

@@

#devtools::install_github("ropenscilabs/umapr")
library(umapr)
embedding <- umapr::umap(sentences_embeddings)

@@

library(RColorBrewer)
brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange()
brewer_list <- list() 
for(i in c(11, 1:nrow(brewer_pal_info_df))){
  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
}
posible_colors <- unlist(brewer_list) %>% unique(brewer_list)  #%>% sample()
posible_colors <- posible_colors[! posible_colors %in% c("#FFFFFF", "#FFFF99", "#E6F598", "#E0E0E0")] # drop white

value_normalized=codings_long_agreed_embeded_subset$value_normalized %>% unique() %>% as.factor()
value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a brewer pallet with lots of values and then assign it to specific values
names(value_normalized_colors) = levels(value_normalized)

# do leaf originals to keep labels for
do_leaf_keep <- codings_long_agreed_embeded_subset %>% dplyr::filter(variable_normalized=="leaf_do_original") %>% dplyr::count(value_normalized) %>% arrange(desc(n)) %>% dplyr::slice_head(n=10)

value_means <- value_means %>% dplyr::mutate(label=ifelse(
  variable_normalized=="leaf_do_original" & !(value_normalized %in% do_leaf_keep$value_normalized), 0, 1))

@@

        facet_wrap( ~ variable_normalized) + 
        theme_bw() +
        theme(legend.position = "none") + 
        geom_label(data=subset(value_means, label==1),
                   aes(x=UMAP1,y=UMAP2, fill = value_normalized, 
                       label=value_normalized, size=50), size = 3, inherit.aes=F, # #variable_normalized_count
                   colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")) + 
        labs(
            title = "Variation in Tags by Semantic Embeddings of Source Sentences",
            subtitle = "Sentences Embedding Sentence-BERT, UMAP Projection ",
            caption = ""
        ) +
       scale_color_manual(values = value_normalized_colors) +
       scale_fill_manual(values = value_normalized_colors)
